---
title: "Creating a 4 x 4 gif of satellite images"
author: "EE Holmes"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

## Creating gifs of satellite images

The script downloads images from the CoastWatch ERDDAP server and then creates a gif using ImageMagick.

Load the packages.  
```{r load_packages}
library(ggplot2) # plotting
library(dplyr) # for %>% pipe
library(purrr) # for map()
library(magick) # for image_* functions
library(stringr) # for the header on images
```



# get the names of each file
imgs=list()
for(j in 1:4){
  year=as.character(years)[j]
  fil_dir <- paste0("pngs/",tag,"_pngs_",year)
  imgs[[j]] = list.files(path = fil_dir, pattern = "*.png", full.names = TRUE)
}

# Then make the gif 4x4
img = c()
imgleg = image_read("pngs/legend.png")
for(i in 1:length(imgs[[1]])){
  theimgs=list()
  for(j in 1:4){
    theimgs[[j]]=image_read(imgs[[j]][i])
    theimgs[[j]] = image_crop(theimgs[[j]], geometry_area(width = 300, height = 332, x_off = 7, y_off = 0))
  }
  imtop <- image_append(image_join(theimgs[[1]],theimgs[[2]]))
  imbot <- image_append(image_join(theimgs[[3]],theimgs[[4]]))
#  imtop <- image_append(image_join(theimgs[[1]],theimgs[[2]],theimgs[[3]],theimgs[[4]],theimgs[[5]]))
#  imbot <- image_append(image_join(theimgs[[6]],theimgs[[7]],theimgs[[8]],theimgs[[9]],theimgs[[10]]))
  im <- magick::image_append(image_join(imtop, imbot, imgleg), stack=TRUE)
  img <- image_join(img, im)
}
imggif = image_animate(img, fps=4, loop=1)
image_write(imggif, paste0("gifs/",tag,"_",years[1],"-",years[4],".gif"))

# 1981:2017 data
# Make legend
require(png)
require(raster)
require(ggplot2)
require(grid)
img <- readPNG(fil) #read in last image
dim_img <- dim(img)
footersize <- 100 #will be different for different pngs
img_height <- dim_img[1]
img_width <- dim_img[2]
png("pngs/sst_legend.png",width=img_width, height=footersize)
grid.raster(img[(img_height-footersize):img_height, 1:img_width, ])
dev.off()


# Then make the gif 
for(year in c(1987,1997,2007)){
  years=year:(year+9)
  # get the names of each file
  imgs=list()
  for(j in 1:10){
    year=as.character(years)[j]
    fil_dir <- paste0("pngs/",tag,"_pngs_",year)
    imgs[[j]] = list.files(path = fil_dir, pattern = "*.png", full.names = TRUE)
  }
img = c()
imgleg = image_read("pngs/sst_legend.png")
for(i in 1:length(imgs[[1]])){
  theimgs=list()
  for(j in 1:10){
    theimgs[[j]]=image_read(imgs[[j]][i])
    theimgs[[j]] = image_crop(theimgs[[j]], geometry_area(width = 300, height = 332, x_off = 7, y_off = 0))
  }
  imtop <- image_append(image_join(theimgs[[1]],theimgs[[2]],theimgs[[3]],theimgs[[4]],theimgs[[5]]))
  imbot <- image_append(image_join(theimgs[[6]],theimgs[[7]],theimgs[[8]],theimgs[[9]],theimgs[[10]]))
  im <- magick::image_append(image_join(imtop, imbot, imgleg), stack=TRUE)
  img <- image_join(img, im)
}
imggif = image_animate(img, fps=4, loop=1)
image_write(imggif, paste0("gifs/",tag,"_",years[1],"-",years[10],".gif"))
}

# Now upload gifs to https://ezgif.com/gif-to-mp4

## More complicated example

I wanted to merge 4 images from 4 years and have a legend at the bottom.  Here's how I did it using ImageMagick to make a big gif (13M) and then uploaded that to ezgif.com to make a much smaller movie.

<div style="text-align:center" markdown="1">

<video width="400" controls>
  <source src="Kochin_SST_2014-17_4x4.mp4" type="video/mp4">
  Your browser does not support HTML5 video.
</video>

## The code

Here is the code I used
```{r make_4x4_movie}
# get the names of each file
imgs=list()
for(j in 1:4){
  year=as.character(2014:2017)[j]
  fil_dir <- paste0("india_sst_pngs_",year)
  imgs[[j]] = list.files(path = fil_dir, pattern = "*.png", full.names = T)
}

# Then make the gif
img = c()
imgleg = image_read("legend.png")
  for(i in 1:length(imgs[[1]])){
    theimgs=list()
    for(j in 1:4){
      theimgs[[j]]=image_read(imgs[[j]][i])
      theimgs[[j]] = image_crop(theimgs[[j]], geometry_area(width = 230, height = 332, x_off = 28, y_off = 0))
    }
    imtop <- image_append(image_join(theimgs[[1]],theimgs[[2]]))
    imbot <- image_append(image_join(theimgs[[3]],theimgs[[4]]))
    im <- magick::image_append(image_join(imtop, imbot, imgleg), stack=TRUE)
    img <- image_join(img, im)
  }
imggif = image_animate(img, fps=4, loop=1)
image_write(imggif, "Kochin_SST_2014-17_4x4.gif")
```

I could also do the same with animation

```{r animation_4x4_movie}
# you can use animation package but the default settings give a low quality movie
library(animation)
library(magick)
imgleg = image_read("legend.png")
saveVideo({
  for(i in 1:length(img14)){
    theimgs=list()
    for(j in 1:4){
      theimgs[[j]]=image_read(imgs[[j]][i])
      theimgs[[j]] = image_crop(theimgs[[j]], geometry_area(width = 230, height = 332, x_off = 28, y_off = 0))
    }
    imtop <- image_append(image_join(theimgs[[1]],theimgs[[2]]))
    imbot <- image_append(image_join(theimgs[[3]],theimgs[[4]]))
    im <- magick::image_append(image_join(imtop, imbot, imgleg), stack=TRUE)
    plot(as.raster(im))
  }
  },
video.name="Kochin_SST_2014-17.mp4"
)
```

