---
title: "Creating a mp4 of satellite images"
author: "EE Holmes"
date: "8/30/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=FALSE)
```

## Creating mp4

This assumes that you already have all the images in a directory.

Load the packages.  
```{r load_packages}
library(ggplot2) # plotting
library(magick) # for image_* functions
library(animation)
```

### Step 1. Install FFmpeg if needed

Here is how to do it on a Mac (MacOS Sierra 10.12.6); Google to figure this out for Windows or Unix.

1. Open up utilities (in apps), and open Terminal.  
2. Type the following on the command line to install `brew`
```
ruby -e "$(curl -fsSL https://raw.github.com/mxcl/homebrew/go/install)"
```
3. Then you can install FFmpeg with this command.
```
brew install ffmpeg
```

### Make animation with FFmpeg

Here is the code to make an animation.

```
fil_dir = "wheremypngsare"
imgs <- list.files(path=fil_dir, pattern="*.png", full.names = TRUE)
animation::saveVideo({
  for(img in imgs){
    im <- magick::image_read(img)
    plot(as.raster(im))
  }
},
video.name="myanimation.mp4"
)
```

The problem is that the mp4 is low quality.  You can change that but you need to dig into the documentation for FFmpeg.

### Use free gif to mp4 converter

Make a gif and then upload to [A free gif to mp4 converter]( https://ezgif.com/gif-to-mp4) like this one.


</div>

